\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath, amssymb, stmaryrd, verbatim} % math symbols
\usepackage{hyperref,nameref,cleveref,enumitem} % for references, hyperlinks
\usepackage[dvipsnames]{xcolor} % Fancy Colours
\usepackage{mathrsfs} % Fancy font
\usepackage{bbm} % mathbb numerals
\usepackage{tikz, tikz-cd, float} % Commutative Diagrams
\usepackage{perpage}
\usepackage{parskip} % So that paragraphs look nice
\usepackage{ifthen,xargs} % For defining better commands
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tgpagella}
\usepackage{cancel}

\title{Plan for analytic stacks project}
\author{Various authors}
\date{May 2025}

\begin{document}

\maketitle

\begin{enumerate}
    \item Light condensed mathematics
    \begin{enumerate}
        \item Light condensed sets
        \begin{enumerate}
          \item Equivalence of light profinite sets,
          metrizable totally disconnected compact Hausdorff,
          and countable Boolean algebras.
          \item Light profinite sets has countable limits.
          \item Non-empty light profinite sets are injective objects in profinite sets.
          \item Profinite set is light iff admits surjection from Cantor set.
          \item Functor from topological spaces to light condensed sets induces : 
          \begin{enumerate}
            \item equivalence on qcqs objects and metrizable compact Hausdorff spaces
            \item equivalence on qs objects and monomorphic ind-completion of
            metrizable compact Hausdorff spaces.
          \end{enumerate}
        \end{enumerate}
        \item Light condensed abelian groups
        \begin{enumerate}
          \item Grothendieck abelian
          \item closed symmetric monoidal
          \item Free functor, symmetric monoidal
          \item Countable products exact
          \item Sequential limits along surjections have surjective projections
          \item Free light condensed abelian group on convergent sequence
          is internally projective.
          \item Prove or disprove : Free light condensed abelian group
          on Cantor set is projective.
          \item $D(\mathrm{Cond}_{\mathbb{N}} \mathrm{Ab}) \simeq 
        \mathrm{Cond}^\wedge_{\mathbb{N}} D(\mathbb{Z})$
          \item Comparison with singular cohomology
        \end{enumerate}
    \end{enumerate}
    \item Analytic rings
    \begin{enumerate}
        \item Light condensed animated rings
        \item Underived pre-analytic structure on a light condensed animated ring.
        Also derived version.
        \item Bijection between underived and derived pre-analytic structures
        \item $\infty$-category of pre-analytic rings has small colimits
        \item analytic rings closed under small sifted colimits
        \item Left adjoint to inclusion of
        analytic rings to pre-analytic rings. 
        Hence analytic rings has all small colimits.
        \begin{enumerate}
            \item Frobenius
            \item Completed symmetric powers
        \end{enumerate}
    \end{enumerate}
    \item Affine theory of non-Archimedean geometry
    \begin{enumerate}
        \item Solid abelian groups
        \begin{enumerate}
            \item Solid groups
            \item Solid gives a non-trivial analytic structure on integers.
            \item Computation of left derived functor of solidification on free objects.
            \item $\mathcal{N}$ is compact projective generator
            for the abelian category of solid modules.
            \item $D(\mathrm{Solid}) \to D(\mathrm{Cond}_{\mathbb{N}} \mathrm{Ab})$
            is fully faithful.
        \end{enumerate}
        \item Huber pairs
        \begin{enumerate}
            \item The analytic ring $\mathbb{Z}[T]_\square$
            \item Given analytic ring $A$ over $\mathbb{Z}_\square$,
            define $A^\circ, A^{\circ\circ} , A^+$
            \item Solid affinoid rings (induced morphism $(A^\triangleright , A^+)_\square \to A$ is an equivalence)
            \item Given a complete Huber ring $A$, adjunction
            between integrally closed subrings $A^+ \subseteq A^\circ$ and
            solid affinoid analytic structures on $A$ as a light condensed ring
            \item Example : $(\mathbb{Z}_p , \mathbb{Z}_p)_\square
            = (\mathbb{Z}_p , \mathbb{Z})_\square \simeq \varprojlim_{n \geq 0} (\mathbb{Z} / p^n , \mathbb{Z})_\square$
            \item Fully faithful functor from complete Huber pairs
            to solid affinoid rings
            \item Tensor product of Tate algebras over $\mathbb{Q}_p$ as analytic rings
        \end{enumerate}
        \item Analytic descent of vector bundles, perfect complexes,
        pseudo-coherent complexes, nuclear objects, compact objects.
        (Andrychev stuff)
        \begin{enumerate}
            \item complete Huber pair is sheafy iff derived structure sheaf is static.
        \end{enumerate}
    \end{enumerate}
    \item Affine theory of complex geometry
    \begin{enumerate}
        \item Gaseous theory 
        \item Liquid theory?
    \end{enumerate}
    \item Analytic stacks
    \begin{enumerate}
        \item Six functor formalisms
        \item !-topology
        \begin{enumerate}
            \item Locale of idempotent algebras for any
            presentable, closed symmetric monoidal, stable $\infty$-category.
            Categorical open immersion, categorical closed immersion.
            \item Proper morphism of affines.
            Iff induced analytic structure
            \item Open immersion of affines.
            \item Canonical factorization of any morphism of affines.
            Notion of !-able morphisms.
            \item !-covers. Lemma for giving !-covers in practice.
            \item Open immersion, proper morphisms, !-able morphisms
            satisfy the theorem for constructing six functor formalisms.
            \item Definition of analytic stacks
        \end{enumerate}
        \item Examples of analytic stacks
        \begin{enumerate}
          \item trivial embedding of sheaves on classical derived affines
          with the countably presented faithfully flat topology.
          \item Fully faithful embedding of adic spaces
          \item Fully faithful embedding from complex analytic spaces
          \item Betti stacks
        \end{enumerate}
    \end{enumerate}
    \item Topics : GAGA theorems
    \begin{enumerate}
        \item non-Archimedean
        \begin{enumerate}
            \item solid analytification
        \end{enumerate}
        \item Archimedean
        \begin{enumerate}
            \item gaseous analytification
        \end{enumerate}
    \end{enumerate}
    \item Topics : analytic de Rham stacks
    \begin{enumerate}
        \item complex analytic Riemann--Hilbert
    \end{enumerate}
    \item Topics : Norms and the gaseous base stack
\end{enumerate}

\end{document}
